\chapter{Description}\label{description}
This section will give the reader an overview of the project, including
why it was conceived, what it will do when complete, and the types of
people we expect will use it. We also list constraints that were faced
during development and assumptions we made about how we would proceed.

The Camelot Server project will create a means of communication between
chat clients, in order to allow end users to communicate with each
other.

\section{Product Perspective}\label{product-perspective}
We have chosen to develop this project in order to create a standard
form of communication between the chat clients that are being developed
to use the server. The developers will use this in order to create an
interface to house the information being transmitted.

\section{Product Functions}\label{product-functions}
The server will have the following capabilities.

\subsection{User Authentication and Login}
Users Will have the option to either create an account or to log in with an existing account.

Users will be able to create accounts by submitting a username that hasn't been taken. The client will send a JSON encoded file that looks something like:

\begin{lstlisting}[style=json]
{
    "tags": {
        "create_account": True
    },
        "create_account": {
        "username": "some username",
            "password": "some password",
        "server_password": "some server password"
    }
}
\end{lstlisting}

If the username has already been taken, then the client will
receive a JSON encoded file that looks something like:

\begin{lstlisting}[style=json]
{
    "tags": {
        "account_creation_success": False
    },
        "message": "Some string"
}
\end{lstlisting}
When the client sends a request to login, it should send a JSON encoded
package to the server. It should look something like this:

\begin{lstlisting}[style=json]
{
    "tags": {
        "login": True
    },
    "login": {
        "username": "some username",
        "password": "some password",
        "server_password": "some server password"
    }
}
\end{lstlisting}

If the username doesn't exist or if the password the user
enters doesn't match the password associated with the user, then the client will receive a JSON encoded file that looks something like:

\begin{lstlisting}[style=json]
{
    "tags": {
        "login_success": False
    },
    "message": "Some string"
}
\end{lstlisting}

There will also be a server password given to each client that the user doesn't have to enter but the client will have to pass along with the user login so that the client can be authenticated.

\subsection{Channels}
\subsubsection{Channel Creation}
As of right now, there will be a set number of channels created by the server that the clients will have the option of joining. Later on in development, we may add the option for users to create channels. Upon creation, the creator will become the admin of that channel. Each user will have a limit on the number of channels they may create.

\subsubsection{Channel Deletion}
As of this writing, only the server team will have the option of deleting specific channels. When users gain the ability to create channels, they will also gain the ability to delete channels that they have created\footnote{The initial channels will be owned by the server team.}.

\subsubsection{Initial Joining of Channels}
After a user has logged in, the server will send the client a list of default channels that the user has the option of joining\footnote{Later on, the user will have the option to search for channels based on a keyword.}. It will look something like this:

\begin{lstlisting}[style=json]
{
    "tags": {
        "login-success": True
    },
     "channels": [
        "channel 1",
        "channel 2",
        "channel 3"
  ]
}
\end{lstlisting}

The client will then need to send back a JSON encoded file to the server describing what channels the user would like to join. The JSON file should look something like this:

\begin{lstlisting}[style=json]
{
    "tags": {
        "joinChannel": True
    },
    "join-channel": [
        "channel 1",
        "other channels they may want to join"
    ]
}
\end{lstlisting}

After the user successfully joins the channels, the specified user will have
access to the channels that they decided to join.

\subsubsection{Joining Channels After Selecting Initial Channels to Join}
Users will have the option to list the channels when logged in. They will be
able to join channels in the same fashion as they did initially\footnote{Later on, the user will have the option to leave channels.}.

\begin{lstlisting}[style=json]
{
    "tags": {
        "newMessage": True
    },
    "channel_receiving_message": "some channel name",
    "message": {
        "user": "the username",
        "timestamp": "the time at which the message was received",
        "message": "the actual message that the user posted"
    }
}
\end{lstlisting}

When a user(client) wishes to send a message to a certain channel, the JSON object should look something like this:

\begin{lstlisting}[style=json]
{
    "tags": {
        "newMessage": True
    },
    "channel_receiving_message": "some channel name",
    "message": {
        "user": "the username",
        "timestamp": "the time at which the message was received",
        "message": "the actual message that the user posted"
    }
}
\end{lstlisting}

Notice that both the JSON file being received by the client and the JSON being sent out by the server look exactly the same. This is done so that the server can simply broadcast messages to all users without having to decode a JSON file server side. This will give the least amount of delay in messages being sent out to each user. Also, the user that sends the message out will also receive the message. It's up to the client in how they want to approach this situation.

\subsection{Send/Receive Messages}
Whenever the server receives notice that a new message has been posted to a given channel, the server will send out a message to each user who is connected to that given channel. The message will be a JSON file that looks something like this:


\section{User Characteristics}\label{user-characteristics}
Most users will be developers who will make clients to interface with
the server. They will be mostly of a more technical background, with
education background involving computer programming. They will be
interfacing with the server in order to create a client for end users to
communicate with each other. They may encounter obstacles with reading
messages if they have no experience with parsing \gls{json}.

\section{General Constraints}\label{general-constraints}
For the constraints of our server, we didn't have any specific
constraints as to what \acrfull{ide} each person used or the platform that they
developed on. The only specific constraints that we have so far is that
the server is going to be developed with \gls{python}3 using \gls{json} for data
transfer and also that each person use \gls{git} for collaborating on the
development of the server. We have not run into any issues with making
our server compatible with other software as of yet.

\section{Assumptions and
Dependencies}\label{assumptions-and-dependencies}
The assumptions made with the development of this project is that each
person that will be working on the server has a working knowledge of
some programming language (most likely \gls{cpp}) and is willing to learn
python. Its also assumed that at least some people working on the server
have some background knowledge as to how to program in python as to help
others within the server group who aren't as familiar with Python.
