\chapter{Specific Requirements}\label{specific-requirements}
The follow sections will go in-depth about the specific requirements of the Camelot system.

\section{User Requirements}\label{user-requirements}
Our user base will be split across two use cases:

\begin{enumerate}
    \item The end users, who will be referred to as the user, and
    \item The client teams, who will be referred as the developers
\end{enumerate}

\subsection{End User Requirements}\label{user-requirements-1}
The user will need to have a client that can connect with the Camelot server. They will need to be able to communicate with other users across channels. They should be able to send and receive messages. Messages should be sent and received in a logical order.

\subsection{Developer Requirements}\label{developer-requirements}
The developers will require the ability to request a list of channels. The list will contain information regarding the channel names and the users currently in each channel. With a successful login, they should be able to create to create a unique user with a specific identifier. Users should be deleted upon signing out or error. The developers should be able to request message information, such as message text, senders, requested channel, and timestamps.

\section{System Requirements}\label{system-requirements}
The Camelot server will be run on a Raspberry Pi 3 Model B. It will need need to have internet access. The hardware will need to have \gls{python}3 installed as well as \gls{postgres} for database management.

\section{Interface Requirements}\label{interface-requirements}
The Camelot will need to interface with a client using \gls{json} formatting as a data transfer protocol.
